---
title: "Marriage Licenses Issued in Canada"
subtitle: "My subtitle if needed"
author: 
  - Aviral Bhardwaj
thanks: "Code and data are available at: https://github.com/Aviral-03/marriage-license-toronto"
date: today
date-format: long
abstract: "Marriage License"
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)


data <- read_csv("../data/analysis_data/analysis_data.csv")

```


# Introduction

The data was collected from Open Data Toronto [@opendata]. The data includes the number of marriage licenses issued in Canada from 2011 to 2024.

This paper explores the number of marriage licenses issued in Canada from 2011 to 2024. Refer to [@sec-data] for the graph that was developed.

We used R [@citeR] programming language to write code. We used libraries [@tidyverse] to clean and analyze the data, and [@ggplot2] to create the graph.

# Data {#sec-data}


```{r}
#| label: fig-marriage
#| fig-cap: Marriage Licenses issued
#| echo: false

data |>
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point() +
  labs(title = "Marriage Licenses Issued",
       x = "Year",
       y = "Licenses")
```

The graph [@fig-marriage] shows that the number of marriage licenses issued in Canada has been increasing over the years. It also shows that there is a seasonal pattern in the number of marriage licenses issued.


\newpage

\appendix

# Appendix {-}

\newpage


# References


